Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Add a TBD
Grammar
Update a comment

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem}
\label{sec:problem}

@@

\begin{quote}
    TBD: introduce \emph{test driver}

    sol: not sure if it is necessary, @mkl, @kazu?
\end{quote}

@@

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
Examples and properties in Haddock comments is automatically
tested by the Doctest command.
Its implementation will be discussed in Section~\ref{sec:doctest}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem}
\label{sec:problem}
\begin{itemize}
    \item TBD: use \emph{code documentation} somewhere here.
\end{itemize}

@@

\begin{quote}
    TBD:

    \begin{itemize}
        \item Do we have to introduce \emph{test driver} here?
        \item Better section titles for all the sections that discuss
            this (problem/solution/implementation).
    \end{itemize}
\end{quote}

@@

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
Examples and properties in Haddock comments are automatically
tested by the Doctest command.
Its implementation will be discussed in Section~\ref{sec:doctest}.
